\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2011-01-20 doc/USER_MANUAL/manual_SPECFEM3D.tex
made changes to the introduction of the manuals

The software package SPECFEM3D simulates seismic
wave propagation at the local or regional scale
based upon the spectral-element method (SEM).
The SEM is a continuous Galerkin technique, which can easily be made discontinous \citep{BeMaPa94,Ch00,KoWoHu02,ChCaVi03,LaWaBe05,Kop06,WiStBuGh10,AcKo11}; it is then a particular case of the discontinuous Galerkin technique \citep{ReHi73,Arn82,FaRi99,HuHuRa99,CoKaSh00,GiHeWa02,RiWh03,MoRi05,GrScSc06,AiMoMu06,BeLaPi06,DuKa06,DeSeWh08,PuAmKa09,WiStBuGh10,DeSe10,EtChViGl10}, with optimized efficiency because of its tensorized basis functions \citep{WiStBuGh10,AcKo11}.
In particular, it can accurately handle very distorted mesh elements \citep{OlSe11}.\\

It has very good convergence and accuracy properties \citep{MaPa89,SePr94,DeFiMu02,Coh02,DeSe07,SeOl08}.
It is also very well suited to parallel implementation on very large supercomputers \citep{KoTr02a,KoTsChTr03,TsKoChTr03,KoLaMi08a,CaKoLaTiMiLeSnTr08,KoViCh10} as well as on clusters of GPU accelerating graphics cards \citep{KoMiEr09,KoErGoMi10,Kom11}. Tensor products inside each element can be optimized to reach very high efficiency \citep{DeFiMu02}, and mesh point and element numbering can be optimized to reduce processor cache misses and improve cache reuse \citep{KoLaMi08a}. The SEM can also handle triangular (in 2D) or tetrahedral (in 3D) elements \citep{WinBoyd96,TaWi00,KoMaTrTaWi01,Coh02,MeViSa06} as well as mixed meshes, although with increased cost and reduced accuracy in these elements, as in the discontinuous Galerkin method.\\

Note that in most geological models in the context of seismic wave propagation studies
(except for fault dynamic rupture studies, in which very high frequencies need to be modeled near the fault, see e.g. \cite{PuAmKa09})
a discontinous mesh is not needed because material property contrasts are not drastic and thus a continuous formulation is sufficient;
conforming mesh doubling bricks can efficiently handle mesh size variations \citep{KoTr02a,KoLiTrSuStSh04}.\\

>>>>

The software package SPECFEM3D simulates seismic
wave propagation at the local or regional scale
based upon the spectral-element method (SEM).
The SEM is a continuous Galerkin technique, which can easily be made discontinous \citep{BeMaPa94,Ch00,KoWoHu02,ChCaVi03,LaWaBe05,Kop06,WiStBuGh10,AcKo11}; it is then close to a particular case of the discontinuous Galerkin technique \citep{ReHi73,Arn82,FaRi99,HuHuRa99,CoKaSh00,GiHeWa02,RiWh03,MoRi05,GrScSc06,AiMoMu06,BeLaPi06,DuKa06,DeSeWh08,PuAmKa09,WiStBuGh10,DeSe10,EtChViGl10}, with optimized efficiency because of its tensorized basis functions \citep{WiStBuGh10,AcKo11}.
In particular, it can accurately handle very distorted mesh elements \citep{OlSe11}.\\

It has very good accuracy and convergence properties \citep{MaPa89,SePr94,DeFiMu02,Coh02,DeSe07,SeOl08}.
It is also very well suited to parallel implementation on very large supercomputers \citep{KoTr02a,KoTsChTr03,TsKoChTr03,KoLaMi08a,CaKoLaTiMiLeSnTr08,KoViCh10} as well as on clusters of GPU accelerating graphics cards \citep{KoMiEr09,KoErGoMi10,Kom11}. Tensor products inside each element can be optimized to reach very high efficiency \citep{DeFiMu02}, and mesh point and element numbering can be optimized to reduce processor cache misses and improve cache reuse \citep{KoLaMi08a}. The SEM can also handle triangular (in 2D) or tetrahedral (in 3D) elements \citep{WinBoyd96,TaWi00,KoMaTrTaWi01,Coh02,MeViSa06} as well as mixed meshes, although with increased cost and reduced accuracy in these elements, as in the discontinuous Galerkin method.\\

Note that in most geological models in the context of seismic wave propagation studies
(except for fault dynamic rupture studies, in which very high frequencies need to be modeled near the fault, see e.g. \cite{PuAmKa09})
a discontinous mesh is not needed because material property contrasts are not drastic and thus a continuous formulation is sufficient;
conforming mesh doubling bricks can efficiently handle mesh size variations \citep{KoTr02a,KoLiTrSuStSh04,LeChLiKoHuTr08,LeChKoHuTr09,LeKoHuTr09}.\\
